---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# codesBR

`codesBR` is a package for adding Brazilian municipal identifiers to a table. Specifically, the package provides simple functions to add IBGE, TSE, and SIAFI identifiers to tables that contain only one of these -- making it simple to match the codes used by public agencies in Brazil to identify each one of the country's 5,570 municipalities. 


## How does it work?

The package's functions are "pipeable" (i.e., can be used in conjunction with `magrittr`'s `%>%`), which makes possible to use it inside a pipe-chain:

```{r pipe, eval=FALSE}
df %>%
  join_codes(id_ibge, "ibge")
```

The package contains two convenience functions to add the two most common identifiers for Brazilian municipalities, from IBGE and TSE. With a variable with IBGE municipal identifiers, to get the correspondent TSE ones use the `tse_from_ibge` function:

```{r tse, eval=FALSE}
# Add TSE identifiers to a table
df <- tse_from_ibge(df, id_tse)
```

Conversely, to get TSE municipal identifiers from IBGE ones, use the `ibge_from_tse` function as follows:

```{r ibge, eval=FALSE}
# Add IBGE identifiers to a table
df <- tse_from_ibge(df, id_ibge)
```


## Installation

To install the development version from GitHub, use:

```{r install github, eval=FALSE}
devtools::install_github("meirelesff/codesBR")
```

## Author

[Fernando Meireles](http://fmeireles.com)


